\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{hyperref}


\title{Final Closure Synthesis:\\
Project Status, Inventories, and Future-Work Gates}
\author{}
\date{2026-02-13}

\begin{document}
\maketitle

\begin{abstract}
This document is the definitive closure synthesis for the
\texttt{physbook} repository.  It supersedes the earlier wind-down snapshot
(2026-02-09) and records: (i)~the project's mission and three-level
program, (ii)~the frozen claim maturity scores for all 17~claims,
(iii)~complete inventories of Lean formalizations, numerical simulations,
theorem notes, and manuscripts, (iv)~the three explicitly deferred
future-work gates, and (v)~reproducibility metadata.  No new theorems are
asserted.
\end{abstract}

\tableofcontents

%% ====================================================================
\section{Project Mission}
%% ====================================================================

The repository investigates how quantum formalism appears when
variational mechanics is made distributionally consistent, through
AI-assisted formal and numerical verification.  The foundational axis has
three cores:
\begin{enumerate}
\item \textbf{Variational-distribution core}: the chain
  $\delta(f') \to \text{action extremals} \to \text{path/field functional
  measure}$ with oscillatory-amplitude interpretation.
\item \textbf{Geometry-of-force bridge}: action reduction yields
  force/orbit/geodesic structure across SR/GR/gauge settings.
\item \textbf{Scale-control core}: refinement/RG/tangent-groupoid
  control ($\tau$-type flow, continuum/de-regularization existence,
  Schwinger--Dyson closure).
\end{enumerate}

%% ====================================================================
\section{Three-Level Program (Goals 1A--1C)}
\label{sec:program}
%% ====================================================================

\begin{description}
\item[Goal~1A (Statics)] Prove consistency for static problems and
  package as a paper on probability amplitudes as geometric
  $\tfrac{1}{2}$-densities.\\
  \emph{Status:} \textbf{Closed.}  Manuscript:
  \texttt{claim1-paper1-static-amplitude-qm-equivalence}.
\item[Goal~1B (Dynamics)] Prove consistency for time-line mechanics and
  package as a path-integral equivalence paper with historical section.\\
  \emph{Status:} \textbf{Closed.}  Manuscript:
  \texttt{claim1-paper2-dynamics-path-integral-equivalence-history}.
\item[Goal~1C (Fields)] Prove consistency for field theory on spacetime
  via a dimension-indexed ladder $d{=}2 \to d{=}3 \to d{=}4$.\\
  \emph{Status:} \textbf{Partially closed.}  The $d{=}2$ ultralocal
  interacting closure is complete; the $d{=}3$ branch is advanced through
  AN-42 (stochastic sub-Gaussian error-budget control); the $d{=}4$
  interacting closure remains open (see~\S\ref{sec:future}).
  Manuscript: \texttt{claim1-paper3-field-theory-general-dimension-roadmap}.
\end{description}

%% ====================================================================
\section{Frozen Claim Maturity Scores}
\label{sec:scores}
%% ====================================================================

Scores are frozen as of 2026-02-13.  The deterministic adjudication rule
(theorem-grade closure, scope widening, or assumption elimination)
produced the final values below.

\subsection{Top~10 Claims}

\begin{longtable}{clcp{7.8cm}}
\toprule
\textbf{Claim} & \textbf{Score} & \textbf{Label} & \textbf{Summary} \\
\midrule
\endfirsthead
\toprule
\textbf{Claim} & \textbf{Score} & \textbf{Label} & \textbf{Summary} \\
\midrule
\endhead
1 & 9.80 & heuristic &
  Scoped theorem package through AN-42: stochastic sub-Gaussian false-stop
  / error-budget control with three-way decomposition
  $\varepsilon = \varepsilon_{\mathrm{reg}} + \varepsilon_{\mathrm{tail}}
  + \varepsilon_{\mathrm{stop}}$ in $d{=}3$ branch.  Full global
  interacting closure remains open. \\
2 & 9.10 & proved &
  SR center-access trichotomy with explicit global turning-set / capture
  map in $n{=}2$ lane. \\
3 & 9.00 & proved &
  Relativistic Coulomb phase portrait: 5-regime taxonomy with
  root/rotation/global-time consistency bridge. \\
4 & 9.20 & proved &
  $n{=}3$ Duffing reduction with robustness windows
  ($|\delta|<0.35$, $\delta_{\mathrm{crit}} \approx -0.697$) and time
  asymptotics. \\
5 & 9.20 & proved &
  D-dimensional GR matching including $D{=}3$ log-potential branch and
  source-normalization crosswalk. \\
6 & 9.60 & proved &
  Schwarzschild fixed-energy interval plus null impact-threshold
  analogue ($b_* = 3\sqrt{3}$). \\
7 & 9.65 & proved &
  ISCO threshold with geometric-to-SI unit crosswalk. \\
8 & 8.15 & heuristic &
  Static/rotating split with effective-potential channel verification
  ($D{=}6$: 93.3\% unstable, 6.7\% narrow stable window).  Full
  all-spin closure open. \\
9 & 8.55 & heuristic &
  Screened-Abelian theorem closure plus first-principles lattice
  plaquette-counting transfer control.  Non-Abelian beyond-window
  transfer and dynamical-matter string-breaking open. \\
10 & 9.65 & proved &
  Circular-orbit benchmark inequalities with deterministic regression
  checks. \\
\midrule
\multicolumn{2}{l}{\textbf{Mean (Claims 1--10)}} & \textbf{9.19} & \\
\bottomrule
\end{longtable}

\subsection{Extended Claims (11--17)}

\begin{longtable}{clcp{7.8cm}}
\toprule
\textbf{Claim} & \textbf{Score} & \textbf{Label} & \textbf{Summary} \\
\midrule
\endfirsthead
\toprule
\textbf{Claim} & \textbf{Score} & \textbf{Label} & \textbf{Summary} \\
\midrule
\endhead
11 & 5.5 & heuristic &
  Planck area quantization forces $3{+}1$ dimensions via inverse-square
  law.  Algebraically verified; propagator-origin step assumed. \\
12 & 5.0 & heuristic &
  Uncertainty principle forces $1/r^2$ force from virtual exchange.
  Correct scaling; $\Delta t = r/c$ ad hoc for massive case. \\
13 & 8.0 & proved &
  Action additivity + composition uniquely forces $\exp(iS/\hbar)$
  kernel, within stated axioms. \\
14 & 7.0 & heuristic &
  Amplitudes as half-densities on tangent-groupoid algebras.  Static
  case proved; infinite-dimensional extension scoped. \\
15 & 4.5 & speculative &
  Democritean refinement argument $\Rightarrow$ quantum mechanics
  necessity.  Mathematically motivated; philosophical rather than
  theorem-grade. \\
16 & 3.5 & speculative &
  Two-body Planck area quantization and standard model mass scales.
  Algebraically explicit; physically speculative. \\
17 & 6.0 & heuristic &
  Schwinger--Dyson identity as RG invariant via Ehrenfest
  correspondence.  Correct in finite-dimensional models. \\
\midrule
\multicolumn{2}{l}{\textbf{Mean (Claims 1--17)}} & \textbf{7.69} & \\
\bottomrule
\end{longtable}

%% ====================================================================
\section{Lean Formalization Inventory}
\label{sec:lean}
%% ====================================================================

Twenty machine-checked modules in \texttt{Claim1lean/}, building on
\texttt{mathlib} (15,798 compiled files).  Toolchain: Lean~4 via
\texttt{elan}; CI via \texttt{.github/workflows/lean.yml}.

\begin{longtable}{lp{9cm}}
\toprule
\textbf{Module} & \textbf{Content} \\
\midrule
\endfirsthead
\toprule
\textbf{Module} & \textbf{Content} \\
\midrule
\endhead
\texttt{Basic.lean} & Utility definitions \\
\texttt{CInvariant.lean} & $c$-invariance under $\tau$ reparameterization \\
\texttt{SmallKappaLipschitz.lean} & $O(\kappa)$ increment inequality on $[0,\kappa]$ \\
\texttt{CovarianceDerivative.lean} & Quotient-derivative identity for $\omega = N/Z$ \\
\texttt{FiniteCovarianceBound.lean} & Finite-support centered-product covariance \\
\texttt{RatioStateDerivativeBound.lean} & Abstract $|\partial\omega|$ bound from AN-7/AN-8 \\
\texttt{RatioStateIncrementBound.lean} & Interval increment bound from derivatives \\
\texttt{FiniteExponentialFamilyDeriv.lean} & Finite-sum exponential-family derivatives \\
\texttt{FiniteExponentialRepresentation.lean} & Centered representation bridge \\
\texttt{FiniteExponentialDerivativeBound.lean} & Model-internal derivative bounds \\
\texttt{FiniteExponentialIncrementBound.lean} & Model-internal $C\kappa$ interval bounds \\
\texttt{FiniteExponentialRegularity.lean} & Automatic regularity (Zsum $> 0$, differentiability) \\
\texttt{WeightedLocalGraphDecay.lean} & Weighted-local truncation, graph-decay, denominator-rate bookkeeping \\
\texttt{SemigroupGenerator.lean} & Semigroup $\to$ generator lemma \\
\texttt{SchurComplementDeterminant.lean} & Schur-complement determinant prefactor template \\
\texttt{SchurComplementElimination.lean} & Block-LDU elimination identity \\
\texttt{GaussianSemigroupNormalization.lean} & 1D Gaussian convolution semigroup prefactor anchor \\
\texttt{GaussianSemigroupNormalizationNd.lean} & Dimension-indexed $d$-power prefactor formulas \\
\texttt{GaussianSemigroupScalingRigidity.lean} & Additive semigroup law fixes prefactor \\
\texttt{VanVleckPrefactorBridge.lean} & $|\det|^{-1/2}$ product identities \\
\bottomrule
\end{longtable}

%% ====================================================================
\section{Manuscript Inventory}
\label{sec:manuscripts}
%% ====================================================================

All manuscripts reside in \texttt{research/workspace/reports/}.

\begin{longtable}{p{6cm}p{8cm}}
\toprule
\textbf{File stem} & \textbf{Content} \\
\midrule
\endfirsthead
\toprule
\textbf{File stem} & \textbf{Content} \\
\midrule
\endhead
\texttt{claim1-paper1-static-\newline amplitude-qm-equivalence} &
  Goal~1A: static variational consistency, probability amplitudes as
  $\tfrac{1}{2}$-densities \\
\texttt{claim1-paper2-dynamics-path-\newline integral-equivalence-history} &
  Goal~1B: dynamics, path-integral chain, historical section \\
\texttt{claim1-paper3-field-theory-\newline general-dimension-roadmap} &
  Goal~1C: dimension-indexed field program with G1/G2/G3 gates \\
\texttt{claim1-scoped-complete-proof} &
  Consolidated Claim~1 scoped theorem chain (static through
  interacting field) \\
\texttt{claim1-variational-delta-note} &
  First statement of Goal~1 as three-level ladder \\
\texttt{claim9-gauge-phase-\newline long-range-paper} &
  Standalone Claim~9: gauge potentials with screened-Abelian closure \\
\texttt{conv-research-program} &
  Overview: what was claimed, what was proved \\
\texttt{newton-action-path-\newline integral-lecture} &
  Foundational narrative: Newton $\to$ action $\to$ path integral \\
\texttt{foundations-refinement-\newline compatibility} &
  Foundations submission: refinement compatibility principle \\
\texttt{winddown-status-snapshot} &
  Earlier wind-down synthesis (now superseded by this document) \\
\texttt{synthesis-proof-dependency} &
  Dependency graph of scoped proof chain \\
\bottomrule
\end{longtable}

%% ====================================================================
\section{Numerical Simulation Inventory}
\label{sec:simulations}
%% ====================================================================

106~Python scripts reside in \texttt{research/workspace/simulations/}.
All referenced diagnostics report \texttt{all\_checks\_pass=True}.
Scripts cover:

\begin{itemize}\item Claim~1 (AN-1 through AN-42): 55+ scripts for continuum,
  $c$-invariance, field-level, envelope, schedule, and stochastic
  checks across $d{=}2$, $d{=}3$, and $d{=}4$ branches.
\item Claims~2--7, 10: orbital mechanics, phase portrait, Duffing,
  GR matching, Schwarzschild, ISCO, and benchmark regression checks.
\item Claim~8 (AB--AF): $D{=}6$ multi-spin discriminant, regime partition,
  margin robustness, outer-branch horizon, effective-potential channel.
\item Claim~9 (AG--AL): non-Abelian transfer positivity, adaptive window,
  budget tightening, segmented cover, Lipschitz budget, first-principles
  transfer derivative control.
\item Claims~11--17: dimensional analysis, uncertainty scaling,
  action-additivity kernel, half-density Born rule, refinement,
  Planck area, SD/RG invariant.
\item Themes~1--2: action-angle EBK cross-check, fermionic mediation
  contact cross-check.
\end{itemize}

%% ====================================================================
\section{Theorem Notes Inventory}
\label{sec:notes}
%% ====================================================================

128~theorem-style notes reside in
\texttt{research/workspace/notes/theorems/}, each with explicit
assumptions, proof, and validation contract.  The notes index is
maintained in \texttt{research/workspace/notes/README.md}.

Audit and tracking files reside in
\texttt{research/workspace/notes/audits/}:
\begin{itemize}\item \texttt{2026-02-08-top10-claim-audit.md} (144~work items, 140 done)
\item \texttt{2026-02-11-extended-claims-audit.md} (Claims 11--17)
\item \texttt{2026-02-10-weekly-score-portfolio.md} (Tasks A--F, all done)
\item \texttt{2026-02-10-weekly-score-retro.md}
\item \texttt{2026-02-10-research-pool-themes.md} (2 themes, deferred)
\end{itemize}

%% ====================================================================
\section{Deferred Future-Work Gates}
\label{sec:future}
%% ====================================================================

The following open proof gates are explicitly deferred at project closure.
Each represents a substantial research program beyond scoped closure.

\subsection{Gate~F1: Claim~1 --- Full $d{=}4$ Interacting Closure}

The $d{=}3$ branch is advanced through AN-42 with stochastic error-budget
control.  Full $d{=}4$ interacting closure requires:
\begin{enumerate}\item G2: continuum existence (ultraviolet renormalization beyond
  superrenormalizable models),
\item G3: reconstruction (recovering Wightman/OS axioms from the
  regulated family).
\end{enumerate}
This is a problem of comparable difficulty to constructive QFT in four
dimensions.

\subsection{Gate~F2: Claim~8 --- $D \ge 6$ All-Spin Rotating Closure}

The static Tangherlini sector and several rotating subclasses are closed
(including the $D{=}6$ doubly-spinning effective-potential channel).  The
remaining open region is a narrow $D{=}6$ stable window (6.7\% of scan
grid) and all $D \ge 7$ multi-spin sectors.  Full closure requires
extending the discriminant/margin analysis to arbitrary spin
configurations in higher dimensions.

\subsection{Gate~F3: Claim~9 --- Non-Abelian Beyond-Window Transfer and
String Breaking}

Screened-Abelian closure is theorem-grade.  Non-Abelian transfer
control has been tightened through AL (first-principles lattice
plaquette-counting bounds), but:
\begin{enumerate}\item beyond-window transfer: weak-coupling cluster-expansion control is
  needed,
\item dynamical-matter string-breaking crossover: requires explicit
  $(G,D,N_f)$-tagged analysis beyond program-level framing.
\end{enumerate}

%% ====================================================================
\section{Items at Closure: In-Progress Lanes}
\label{sec:inprogress}
%% ====================================================================

Two work items from the audit remain marked \texttt{[in progress]} at
closure:

\begin{enumerate}
\item \textbf{Item~96 (Physarticle scan backlog)}: remaining targets
  include half-density scalarization unitarity, full Gaussian kernel
  $t^{-d/2}$ semigroup normalization in $d$~dimensions (kernel-level),
  point-splitting $\delta'$ lemma, and Planck-area hypothesis cleanup.
  \emph{Deferred.}
\item \textbf{Item~105 (Newton-limit paradox support)}: next target is
  the kernel-level semigroup/normalization constraint behind
  Gaussian/Van-Vleck prefactors and its link to amplitude/half-density
  necessity.  \emph{Deferred.}
\end{enumerate}

Two bibliography anchors (Item~97: \texttt{Connes1994},
\texttt{Landsman1998}) remain \texttt{PENDING}.  \emph{Deferred.}

%% ====================================================================
\section{Research Pool Themes}
\label{sec:themes}
%% ====================================================================

Two non-core themes were queued but are \textbf{deferred at closure}:
\begin{enumerate}
\item \textbf{Theme~1}: action--angle ``undeterminacy'' for central
  potentials.  Initial deliverable (Coulomb EBK cross-check) completed;
  full formalization deferred.
\item \textbf{Theme~2}: fermionic field mediation of central potentials.
  Initial deliverable (contact-interaction cross-check) completed;
  full formalization deferred.
\end{enumerate}

%% ====================================================================
\section{Repository Consistency Checks}
\label{sec:consistency}
%% ====================================================================

\begin{itemize}\item \textbf{Git state}: clean (only \texttt{.DS\_Store} uncommitted).
  No open PRs or issues.
\item \textbf{Lean CI}: last run passed; 15,798/15,798 files compiled.
\item \textbf{Simulation diagnostics}: all 106 scripts report
  \texttt{all\_checks\_pass=True} as documented in audit trail.
\item \textbf{Audit trail}: top-10 audit has 144 work items (140 done,
  2 in-progress now deferred, 1 queued now deferred, 1 score-update done).
  Weekly portfolio tasks A--F all completed.
\item \textbf{Score consistency}: scores in
  \texttt{top10-claim-audit.md}, \texttt{weekly-score-portfolio.md}, and
  this document are mutually consistent at $\bar{S}=9.19$.
\end{itemize}

%% ====================================================================
\section{Validation Contract}
%% ====================================================================

\subsection*{Assumptions}
\begin{enumerate}\item This is a status synthesis; no new theorem is claimed.
\item All closure/open labels are inherited from tracked artifacts.
\end{enumerate}

\subsection*{Units and Dimensions}
No new dimensional claim is introduced.

\subsection*{Symmetry/Conservation}
No new symmetry or conservation claim is asserted.

\subsection*{Independent Cross-Check Path}
\begin{enumerate}\item Compare score tables across audit, portfolio, and this document.
\item Verify Lean module list against \texttt{ls Claim1lean/}.
\item Verify simulation count against \texttt{ls simulations/ | wc -l}.
\end{enumerate}

\subsection*{Confidence}
High confidence for inventory extraction and score consistency.  Medium
confidence for completeness of the deferred-gate descriptions, which
summarize open research problems.

%% ====================================================================
\section{Reproducibility Metadata}
%% ====================================================================

\begin{itemize}\item Date anchor: 2026-02-13 (US).
\item Repository: \texttt{/Users/arivero/physbook}, branch \texttt{main}.
\item Lean toolchain: Lean~4 via \texttt{elan}, mathlib dependency.
\item Python: 3.12 with numpy, scipy, sympy, matplotlib.
\item \TeX: TeX Live 2025 (\texttt{pdflatex}).
\item This document supersedes
  \texttt{2026-02-09-winddown-status-snapshot.tex}.
\end{itemize}

\end{document}
