\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}
\usepackage{upquote}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\title{Phase-Resolved Long-Range Gauge Potentials:\\
Screened-Abelian Closure and Confining/Coulomb Program}
\author{}
\date{2026-02-09}

\begin{document}
\maketitle

\begin{abstract}
This paper isolates Claim 9 into assumption-explicit sectors instead of a single
``generic gauge'' statement. We provide a theorem-grade closure for the screened
Abelian branch in arbitrary spacetime dimension, including the exact Yukawa kernel
and its large-distance asymptotic. We also close a scoped non-Abelian extraction
theorem: under explicit \((SU(N),D)\) area-law-plus-perimeter hypotheses, finite-\(T\)
Wilson-loop extraction converges to a linear potential with quantitative error
bounds. In addition, we derive that hypothesis package inside an explicit
strong-coupling lattice window for \(SU(N)\). Remaining open gaps are extending
that derivation beyond the strong-coupling window via transfer assumptions and
closing dynamical-matter string-breaking rigor.
\end{abstract}

\section{Scope}

\subsection*{In-scope claim}
\begin{enumerate}
\item phase-conditioned static potential classification by Wilson-loop asymptotics,
\item theorem-grade screened-Abelian branch with explicit dimension dependence,
\item scoped non-Abelian finite-\(T\) extraction theorem under explicit \((G,D)\)-tagged assumptions,
\item scoped derivation of those non-Abelian assumptions in a strong-coupling lattice window,
\item scoped \(\beta\)-transfer theorem extending that assumption package to a wider \(\beta\)-window.
\end{enumerate}

\subsection*{Out of scope}
\begin{enumerate}
\item universal phase diagram across all gauge groups and matter contents,
\item claiming non-Abelian continuum confinement closure beyond the stated strong-coupling window.
\end{enumerate}

\section{Setup}

Let \(G\) be the gauge group, \(D\) spacetime dimension, and \(n=D-1\) spatial dimension.
Define static potential by rectangular Wilson loops:
\[
\langle W(r,T)\rangle \sim e^{-V(r)T},\qquad T\to\infty.
\]
Long-range classification concerns asymptotics of \(V(r)\) as \(r\to\infty\).

\subsection*{Goal-9 Dependency Declaration}
We treat Claim 9 as
\[
\mathrm{Goal9}(G,D;\text{phase},\text{matter}).
\]
No statement is promoted unless both dependencies are explicit:
\begin{enumerate}
\item gauge-group/model dependency \(G\) (for example \(U(1)\), \(SU(N)\), \(SU(N)\)+fundamental matter),
\item spacetime-dimension dependency \(D\).
\end{enumerate}

\subsection*{Dependency Matrix (Current Program State)}
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
\((G,\text{matter},\text{phase})\) & \(D\)-dependence & Asymptotic claim & Status \\
\hline
\((U(1),\ \text{none},\ \text{Coulomb})\) & explicit in all \(D\) & \(r,\log r,r^{3-D}\) & proposition \\
\hline
\((U(1),\ \text{Higgs},\ \text{screened})\) & explicit in all \(D\) & \(r^{-(D-2)/2}e^{-mr}\) & theorem \\
\hline
\((SU(N),\ \text{none},\ \text{confining})\) & explicit \((G,D)\), finite-window \(r,T\), strong-coupling + \(\beta\)-transfer lanes & linear extraction with \(O(T^{-1})\) bounds & scoped theorem + scoped derivation \\
\hline
\((SU(N),\ N_f>0,\ \text{string-breaking})\) & dimension-tagged, model dependent & linear-to-saturation crossover & program \\
\hline
\end{tabular}
\end{center}

\section{Phase-Conditioned Statements}

\begin{proposition}[Massless Coulomb-class sector \((G=U(1),D)\)]
Assume gauge group \(G=U(1)\), Coulomb phase, and a massless unscreened gauge mode in \(n\) dimensions.
Then
\[
V_{\mathrm{Coul}}(r)\propto g^2 C\,\Phi_n(r),
\]
where \(\Phi_n\) is the Laplacian Green kernel and
\[
\Phi_n(r)\sim
\begin{cases}
r, & n=1\ (D=2),\\
\log r, & n=2\ (D=3),\\
r^{2-n}, & n>2\ (D\ge4).
\end{cases}
\]
\end{proposition}

\begin{theorem}[Screened-Abelian Yukawa branch \((G=U(1),m>0,D)\)]
Let \(G=U(1)\), \(m>0\), \(n=D-1\ge1\), and
\[
(-\Delta+m^2)G_{n,m}=\delta_0
\]
in \(\mathbb{R}^n\), with \(G_{n,m}(r)\to0\) as \(r\to\infty\). Then
\[
G_{n,m}(r)=\frac{1}{(2\pi)^{n/2}}\left(\frac{m}{r}\right)^\nu K_\nu(mr),
\qquad
\nu=\frac n2-1,
\]
and as \(r\to\infty\),
\[
G_{n,m}(r)=
\frac{1}{2(2\pi)^{(n-1)/2}}
m^{(n-3)/2}r^{-(n-1)/2}e^{-mr}
\left(1+O(r^{-1})\right).
\]
For static charges \(q_1,q_2\), \(V(r)=q_1q_2G_{n,m}(r)\), hence
\[
V(r)\sim r^{-(D-2)/2}e^{-mr},
\]
so the inter-source term decays exponentially and the large-\(r\) energy saturates
to an \(r\)-independent baseline.
\end{theorem}

\begin{proof}[Proof sketch]
Use Fourier representation
\[
G_{n,m}(x)=\frac{1}{(2\pi)^n}\int_{\mathbb R^n}\frac{e^{ik\cdot x}}{|k|^2+m^2}\,dk,
\]
radial reduction, and the standard Hankel/Bessel identity to obtain the exact kernel.
Then apply \(K_\nu(z)\sim \sqrt{\pi/(2z)}\,e^{-z}(1+O(z^{-1}))\) as \(z\to+\infty\).
The exponential factor yields saturation of the interaction contribution.
\end{proof}

\begin{proposition}[Confining area-law sector \((G=SU(N),N\ge2,D)\)]
Assume gauge group \(G=SU(N)\) with \(N\ge2\), in a pure-gauge confining regime with
\[
\langle W(r,T)\rangle \sim e^{-\sigma rT},\qquad \sigma>0.
\]
Then the static potential obeys
\[
V_{\mathrm{conf}}(r)\sim \sigma r
\]
in the corresponding large-\(r\) regime.
\end{proposition}

\begin{theorem}[Strong-coupling derivation lane for AB hypotheses \((G=SU(N),N\ge2,D)\)]
Fix \((G,D)=(SU(N),D)\), \(N\ge2\), and Wilson lattice action with spacing \(a\),
\[
S_W(U)=-\frac{\beta}{N}\sum_p \Re\mathrm{Tr}(U_p),\qquad 0<\beta\le\beta_{\mathrm{sc}}.
\]
For rectangles \(C(r,T)\), write \(A(C)=rT/a^2\), \(P(C)=2(r+T)/a\), and assume
\[
\log\langle W(C)\rangle
=
-\sigma_{\mathrm{sc}}(\beta)A(C)
+\pi_{\mathrm{sc}}(\beta)P(C)
+\delta_{\mathrm{sc}}(C;\beta),
\]
with \(\sigma_{\mathrm{sc}}(\beta)>0\), \(|\delta_{\mathrm{sc}}(C;\beta)|\le C_{\mathrm{sc}}(\beta)\),
and \(0<\langle W(C)\rangle<1\) in the extraction window.
Define
\[
\sigma_D=\frac{\sigma_{\mathrm{sc}}(\beta)}{a^2},\qquad
p_D=\frac{2\pi_{\mathrm{sc}}(\beta)}{a},\qquad
c_D=0,\qquad
\varepsilon_D(r,T):=\delta_{\mathrm{sc}}(C(r,T);\beta).
\]
Then AB assumptions hold in this explicit model class:
\[
\log\langle W(r,T)\rangle
=
-\sigma_D rT+p_D(r+T)+c_D+\varepsilon_D(r,T),\qquad
|\varepsilon_D(r,T)|\le C_{\mathrm{sc}}(\beta).
\]
\end{theorem}

\begin{proof}[Proof sketch]
Substitute \(A(C)\), \(P(C)\) into the assumed strong-coupling form and collect
channels \(rT\), \(r+T\), and bounded residual.
\end{proof}

\begin{theorem}[Beyond-window transfer lane for AB hypotheses \((G=SU(N),N\ge2,D)\)]
Fix an anchor \(\beta_0\in(0,\beta_{\mathrm{sc}}]\) where AB hypotheses are known.
Assume for \(\beta\in[\beta_0,\beta_1]\):
\[
\partial_\beta\log\langle W(r,T)\rangle_\beta
=
-a_\beta\,rT+b_\beta\,(r+T)+R_\beta(r,T),
\]
with
\[
|a_\beta|\le A_*,\qquad |b_\beta|\le B_*,\qquad |R_\beta(r,T)|\le R_*.
\]
If
\[
\log\langle W(r,T)\rangle_{\beta_0}
=
-\sigma_0rT+p_0(r+T)+\varepsilon_0(r,T),\qquad |\varepsilon_0|\le C_0,
\]
then for all \(\beta\in[\beta_0,\beta_1]\),
\[
\log\langle W(r,T)\rangle_\beta
=
-\sigma(\beta)\,rT+p(\beta)\,(r+T)+\varepsilon_\beta(r,T),
\]
where
\[
\sigma(\beta)=\sigma_0+\int_{\beta_0}^{\beta}a_s\,ds,\qquad
p(\beta)=p_0+\int_{\beta_0}^{\beta}b_s\,ds,
\]
\[
\varepsilon_\beta(r,T)=\varepsilon_0(r,T)+\int_{\beta_0}^{\beta}R_s(r,T)\,ds,
\]
and
\[
|\sigma(\beta)-\sigma_0|\le A_*|\beta-\beta_0|,\qquad
|p(\beta)-p_0|\le B_*|\beta-\beta_0|,\qquad
|\varepsilon_\beta(r,T)|\le C_0+R_*|\beta-\beta_0|.
\]
\end{theorem}

\begin{proof}[Proof sketch]
Integrate the \(\beta\)-derivative decomposition between \(\beta_0\) and \(\beta\),
then apply uniform bounds on \(a_\beta,b_\beta,R_\beta\).
\end{proof}

\begin{theorem}[Scoped non-Abelian linear extraction \((G=SU(N),N\ge2,D)\)]
Fix \((G,D)=(SU(N),D)\), \(N\ge2\), and \(r\in[r_{\min},r_{\max}]\), \(T\ge T_0\).
Assume constants \(\sigma_D>0\), \(p_D\), \(c_D\), \(C_D\) such that
\[
\log\langle W(r,T)\rangle
=
-\sigma_D rT
+p_D(r+T)
+c_D
+\varepsilon_D(r,T),
\qquad
|\varepsilon_D(r,T)|\le C_D.
\]
Then
\[
V(r;T)=\sigma_D r-p_D-\frac{p_Dr+c_D+\varepsilon_D(r,T)}{T},
\]
hence
\[
\left|V(r;T)-(\sigma_D r-p_D)\right|
\le
\frac{|p_D|r+|c_D|+C_D}{T}.
\]
For \(r_1<r_2\) in the same window, with
\[
S_T(r_1,r_2):=\frac{V(r_2;T)-V(r_1;T)}{r_2-r_1},
\]
one has
\[
\left|S_T(r_1,r_2)-\sigma_D\right|
\le
\frac{|p_D|}{T}
+
\frac{2C_D}{T(r_2-r_1)}.
\]
\end{theorem}

\begin{proof}[Proof sketch]
Insert the assumed logarithmic form into \(V(r;T)=-(1/T)\log\langle W(r,T)\rangle\),
separate linear and remainder channels, and bound with \(|\varepsilon_D|\le C_D\).
For the slope estimate, subtract the two \(r\)-values and use
\(|\varepsilon_D(r_2,T)-\varepsilon_D(r_1,T)|\le2C_D\).
\end{proof}

\begin{proposition}[Dynamical-fundamental matter crossover \((G=SU(N),N_f>0,D)\)]
Assume gauge group \(G=SU(N)\) with \(N_f>0\) dynamical fundamental flavors and pair creation/string breaking dynamically allowed.
Then one expects:
\begin{enumerate}
\item approximately linear behavior \(V(r)\sim \sigma r\) at intermediate \(r\),
\item crossover to saturation at sufficiently large \(r\).
\end{enumerate}
\end{proposition}

\begin{corollary}[Claim 9 status in this paper]
Within the screened-Abelian class \((G=U(1),m>0)\), Claim 9 is theorem-closed
with explicit \(D\)-dependence. In the confining non-Abelian branch
\((G=SU(N),D)\), finite-\(T\) linear extraction is now theorem-closed in a scoped
\((r,T)\)-window under explicit area-law-plus-perimeter assumptions, and those
assumptions are now derived in a scoped strong-coupling lattice window and
extended by an explicit \(\beta\)-transfer theorem to a wider parameter window.
The remaining open gaps are first-principles control of transfer assumptions and
full dynamical-matter string-breaking crossover theorems.
\end{corollary}

\section{Literature Anchors}

\begin{enumerate}
\item Wilson and Kogut (1974), RG/phase framing:
\href{https://doi.org/10.1016/0370-1573(74)90023-4}{doi:10.1016/0370-1573(74)90023-4}.
\item Osterwalder and Schrader I (1973), Euclidean axioms:
\href{https://doi.org/10.1007/BF01645738}{doi:10.1007/BF01645738}.
\item Osterwalder and Schrader II (1975), reconstruction:
\href{https://doi.org/10.1007/BF01608978}{doi:10.1007/BF01608978}.
\item Fradkin and Shenker (1979), phase continuity in lattice gauge-Higgs systems:
\href{https://doi.org/10.1103/PhysRevD.19.3682}{doi:10.1103/PhysRevD.19.3682}.
\item Kogut (1979), lattice gauge theory review (strong-coupling background):
\href{https://doi.org/10.1103/RevModPhys.51.659}{doi:10.1103/RevModPhys.51.659}.
\item Seiler (1982), Gauge Theories as a Problem of Constructive Quantum Field Theory:
\href{https://doi.org/10.1007/978-3-540-39023-7}{doi:10.1007/978-3-540-39023-7}.
\end{enumerate}

\section{Validation Contract}

\subsection*{Assumptions}
\begin{enumerate}
\item each statement is conditioned on explicit \((G,D)\), phase, and matter tags,
\item screened-Abelian closure uses \(m>0\) and linearized static kernel framework,
\item scoped non-Abelian theorem uses explicit finite-window area-law/perimeter hypotheses.
\end{enumerate}

\subsection*{Units and dimensions check}
\begin{enumerate}
\item \(mr\) is dimensionless in Yukawa factors,
\item dimensional prefactors in \(G_{n,m}\) match the \(n=D-1\) Green-kernel scaling.
\end{enumerate}

\subsection*{Independent cross-check paths}
\begin{enumerate}
\item analytic Green-kernel and asymptotic derivation (this paper),
\item executable checks:
\begin{itemize}
\item \texttt{python3.12 research/workspace/simulations/claim9\_phase\_longrange\_table.py},
\item \texttt{python3.12 research/workspace/simulations/claim9\_model\_class\_table.py},
\item \texttt{python3.12 research/workspace/simulations/claim9\_abelian\_screened\_asymptotic\_check.py},
\item \texttt{python3.12 research/workspace/simulations/claim9\_nonabelian\_arealaw\_linear\_check.py},
\item \texttt{python3.12 research/workspace/simulations/claim9\_nonabelian\_strong\_coupling\_window\_check.py},
\item \texttt{python3.12 research/workspace/simulations/claim9\_nonabelian\_beyond\_window\_transfer\_check.py}.
\end{itemize}
\end{enumerate}

\subsection*{Confidence statement}
Screened-Abelian long-range behavior is theorem-grade in this scoped class.
The confining non-Abelian extraction lane is now theorem-grade under explicit
\((G,D)\)-tagged finite-window assumptions, and those assumptions are derived in
a scoped strong-coupling lattice window with an explicit \(\beta\)-transfer lane.
First-principles control beyond this scoped transfer model and closing
string-breaking with dynamical matter remain open.

\section{Reproducibility Metadata}

\begin{itemize}
\item date anchor: 2026-02-09 (US),
\item build toolchain tested here: \texttt{/Library/TeX/texbin/pdflatex} (TeX Live 2025),
\item safe build script:
\texttt{\textasciitilde/.codex/skills/pdflatex-safe-build/scripts/build\_pdflatex\_safe.sh}.
\end{itemize}

\section{Conclusion}

Claim 9 should be read as phase-resolved, not universal.
The screened-Abelian branch is fully closed at theorem level in this manuscript.
The non-Abelian confining branch is now closed at scoped extraction-theorem level
under explicit \((G,D)\)-tagged area-law/perimeter assumptions, with a scoped
derivation lane grounded in an explicit strong-coupling lattice model and
extended by an explicit \(\beta\)-transfer theorem.
First-principles control of the transfer assumptions and full string-breaking
crossover remain explicit \((G,D)\)-indexed next targets.

\end{document}
